Splitting It Up: The \pkg{spduration} Split-Population Duration Regression Package for Time-varying Covariates

### 2017-06-24 R Journal/beger-hill-metternich-minhas-ward.tex
added short paragraph

>>>>

Additionally, risk factors might change over time which requires estimators 
that can account for such dynamics. We therefore present a split-population 
estimator that allows for the inclusion of time-varying covariates, which is an 
important distinction to other R implementations of split-population or cure models.
